A hazards approach to the biometric analysis of infant mortality

### 2023-03-12 paper2.Rmd
minor adjustment
References added

In this version the cumulative hazard functions are depicted as-is, but on the
log-cube time scale. See the new **R** function *drawBB2*.

@@

Instead of using the total number of births throughout in the denominator as in  the
Bourgeois-Pichat procedure, we suggest 
using the present risk-set size, that is, the the total number of infants still alive 
immediately prior to the death age under investigation. Given proper data, it is easily achieved.
For instance,by the use of 
the function `risksets` in the **R** package `eha` we can get Table \@ref(tab:risksets).

@@

This is an interesting case because it appears as if the data quality is low since 
the linearity during the post-neonatal period is gone. Rather, there is a "hockey-stick" pattern, 
also seen in other old data sets. See Figure \@ref(fig:scahigh).

>>>>

@@

Instead of using the total number of births throughout in the denominator as in  the
Bourgeois-Pichat procedure, we suggest 
using the present risk-set size, that is, the the total number of infants still alive 
immediately prior to the death age under investigation. Given proper data, it is easily achieved.
For instance,by the use of 
the function `risksets` in the **R** [@cran] package `eha` [@eha; @ehar2] we can get Table \@ref(tab:risksets).

@@

The Scanian dataset covers five parishes in Scania 1720--1810 [@sedd].
It is an interesting case because it appears as if the data quality is low since 
the linearity during the post-neonatal period is gone. Rather, there is a "hockey-stick" pattern, 
also seen in other old data sets. See Figure \@ref(fig:scahigh).
